The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-20 manuscript.Rmd
[fix #19] more mentions about other studies

<!--  study focused on USA but conclusions more general given that it's arguably one of the better studied area + data availability -->
<!-- * barcoding has shown that typically marine invertebrates are complex of cryptic species with small ranges; therefore potentially more vulnerable to extinction risk. -->
<!-- * need collaboration among researchers to share data standards, protocols -->
<!-- * use existing knowledge to fill missing gaps -->
<!-- * running against time -->
<!-- * we need to document species diversity better for conservation (knowing what we protect and to measure the effectiveness of the protection) -->
<!-- * how do we conserve animal species that we can't see, we don't find pretty, don't have eyes -->
<!-- * recent advances in technologies make possibility of developing a global monitoring program possible: reduced costs of sequencing, detection of rare species, etc.... -->
<!-- * Using this kind of approaches at a large scale might also be a good way to have a better sense of how much of the biodiversity we are missing. -->
<!-- * Most species are rare, especially in very diverse places,  and the degradation of habitats makes it even more difficult to find these rare species. -->

@@

The continental US includes a wide diversity of marine ecosystems from the Florida Keys, to the Gulf of Maine on the East Coast; and from the arid Southern California to the oceanic coast of the Pacific Northwest. With estuaries, bays, sandy beaches, rocky shores, and coral reefs, the US coastlines harbors many biotas. While the continental shelf extends for several hundred kilometers on the East coast, it is narrow on the West coast. This diversity of habitats and depths, combined with the exploitation of natural resources as early as the 1880, has led to extensive exploration and documentation of marine biodiversity [@Fautin2010]. However, apart from the synthesis that emerged from the Census of Marine Life efforts [@Fautin2010], no study has attempted to synthesize the current state of knowledge of marine biodiversity across the continental US.

>>>>

<!-- * how do we conserve animal species that we can't see, we don't find pretty, don't have eyes -->
<!-- * Most species are rare, especially in very diverse places,  and the degradation of habitats makes it even more difficult to find these rare species. -->

@@

Here, we focus on the continental US because the marine biodiversity is extensively documented as the result of a long history of studies by governmental, academic, and private institutions [@Fautin2010]. The continental US includes a wide diversity of marine ecosystems from the Florida Keys, to the Gulf of Maine on the East Coast; and from the arid Southern California to the oceanic coast of the Pacific Northwest on the West coast. With estuaries, bays, sandy beaches, rocky shores, and coral reefs, the US coastlines harbors many biotas. While the continental shelf extends for several hundred kilometers on the East coast, it is narrow on the West coast. This diversity of habitats and bathymetric profiles, combined with efforts at the national level to make data publicly available, make this region especially suitable to evaluate how much we know about marine biodiversity using biodiversity databases. However, apart from the syntheses that emerged from the Census of Marine Life efforts [@Costello2010,@Fautin2010], no study has yet attempted to synthesize the current state of knowledge of marine biodiversity across the continental US, and this study is the first using data from public databases.
